---
title: "Chapter 10 Problem 9"
author: "Andira Putri"
output: pdf_document
---

#### Consider the `USArrests` data. We will now perform hierarchical clustering on the states.

#### a.) Using hierarchical clustering with complete linkage and Euclidean distance, cluster the states.

```{r}
df=USArrests
hc.comp=hclust(dist(df),method="complete")
plot(hc.comp,main="Complete Linkage",xlab="",sub="",cex=0.9,hang=-1)
```

#### b.) Cut the dendrogram at a height that results in three distinct clusters. Which states belong to which clusters?

```{r}
cutree(hc.comp,3)
table(cutree(hc.comp,3))
```

#### c.) Hierarchically cluster the states using complete linkage and Euclidean distance, after scaling the variables to have standard deviation one.

```{r}
df.scaled=scale(df)
hc.comp.sc=hclust(dist(df.scaled),method="complete")
plot(hc.comp.sc,main="Complete Linkage -- Scaled",xlab="",sub="",cex=0.9,hang=-1)
```

#### d.) What effect does scaling the variables have on the hierarchical clustering obtained? In your opinion, should the variables be scaled before the inter-observation dissimilarities are computed? Provide a justification for your answer?

```{r}
cutree(hc.comp.sc,3)
table(cutree(hc.comp.sc,3))
```